
\sect{Habakkuk (LXX)}

\subsect{Chapter 1}

\versification{1}
τὸ
λῆμμα\footnote{λἠμμα - oracle, contents of what was given to the prophet}
ὃ
εἶδεν
᾿Αμβακοὺμ
ὁ
προφήτης. -
\versification{2}
῞Εως
τίνος,\footnote{ἕως τίνος - how long?}
Κύριε,
κεκράξομαι
καὶ
οὐ
μὴ
εἰσακούσῃς;
βοήσομαι
πρός
σε
ἀδικούμενος
καὶ
οὐ
σώσεις;
\versification{3}
ἵνα
τί
ἔδειξάς
μοι
κόπους
καὶ
πόνους,
ἐπιβλέπειν
ταλαιπωρίαν
καὶ
ἀσέβειαν;
ἐξεναντίας
μου
γέγονε
κρίσις,
καὶ
ὁ
κριτὴς
λαμβάνει.
\versification{4}
διὰ
τοῦτο
διεσκέδασται
νόμος,
καὶ
οὐ
διεξάγεται
εἰς
τέλος
κρίμα,
ὅτι
ὁ
ἀσεβὴς
καταδυναστεύει
τὸν
δίκαιον·
ἕνεκεν
τούτου
ἐξελεύσεται
τὸ
κρίμα
διεστραμμένον.
\versification{5}
ἴδετε,
οἱ
καταφρονηταί,
καὶ
ἐπιβλέψατε
καὶ
θαυμάσατε
θαυμάσια
καὶ
ἀφανίσθητε,
διότι
ἔργον
ἐγὼ
ἐργάζομαι
ἐν
ταῖς
ἡμέραις
ὑμῶν,
ὃ
οὐ
μὴ
πιστεύσητε,
ἐάν
τις
ἐκδιηγῆται.
\versification{6}
διότι
ἰδοὺ
ἐγὼ
ἐξεγείρω
ἐφ᾿
ὑμᾶς
τοὺς
Χαλδαίους
τοὺς
μαχητάς,
τὸ
ἔθνος
τὸ
πικρὸν
καὶ
τὸ
ταχινόν,
τὸ
πορευόμενον
ἐπὶ
τὰ
πλάτη
τῆς
γῆς
τοῦ
κατακληρονομῆσαι
σκηνώματα
οὐκ
αὐτοῦ.
\versification{7}
φοβερὸς
καὶ
ἐπιφανής
ἐστιν,
ἐξ
αὐτοῦ
τὸ
κρίμα
αὐτοῦ
ἔσται
καὶ
τὸ
λῆμμα
αὐτοῦ
ἐξ
αὐτοῦ
ἐξελεύσεται.
\versification{8}
καὶ
ἐξαλοῦνται
ὑπὲρ
παρδάλεις
οἱ
ἵπποι
αὐτοῦ
καὶ
ὀξύτεροι
ὑπὲρ
τοὺς
λύκους
τῆς
᾿Αραβίας·
καὶ
ἐξιππάσονται
οἱ
ἱππεῖς
αὐτοῦ
καὶ
ὁρμήσουσι
μακρόθεν
καὶ
πετασθήσονται
ὡς
ἀετὸς
πρόθυμος
εἰς
τὸ
φαγεῖν.
\versification{9}
συντέλεια
εἰς
ἀσεβεῖς
ἥξει,
ἀνθεστηκότας
προσώποις
αὐτῶν
ἐξεναντίας
καὶ
συνάξει
ὡς
ἄμμον
αἰχμαλωσίαν.
\versification{10}
καὶ
αὐτὸς
ἐν
βασιλεῦσιν
ἐντρυφήσει
καὶ
τύραννοι
παίγνια
αὐτοῦ,
καὶ
αὐτὸς
εἰς
πᾶν
ὀχύρωμα
ἐμπαίξεται
καὶ
βαλεῖ
χῶμα
καὶ
κρατήσει
αὐτοῦ.
\versification{11}
τότε
μεταβαλεῖ
τὸ
πνεῦμα
καὶ
διελεύσεται
καὶ
ἐξιλάσεται·
αὕτη
ἡ
ἰσχὺς
τῷ
Θεῷ
μου.
\versification{12}
οὐχὶ
σὺ
ἀπ᾿
ἀρχῆς,
Κύριε,
ὁ
Θεὸς
ὁ
ἅγιός
μου;
καὶ
οὐ
μὴ
ἀποθάνωμεν.
Κύριε,
εἰς
κρίμα
τέταχας
αὐτόν·
καὶ
ἔπλασέ
με
τοῦ
ἐλέγχειν
παιδείαν
αὐτοῦ.
\versification{13}
καθαρὸς
ὁ
ὀφθαλμὸς
τοῦ
μὴ
ὁρᾶν
πονηρά,
καὶ
ἐπιβλέπειν
ἐπὶ
πόνους
οὐ
δυνήσῃ·
ἵνα
τί
ἐπιβλέπεις
ἐπὶ
καταφρονοῦντας;
παρασιωπήσῃ
ἐν
τῷ
καταπίνειν
ἀσεβῆ
τὸν
δίκαιον;
\versification{14}
καὶ
ποιήσεις
τοὺς
ἀνθρώπους
ὡς
τοὺς
ἰχθύας
τῆς
θαλάσσης
καὶ
ὡς
τὰ
ἑρπετὰ
τὰ
οὐκ
ἔχοντα
ἡγούμενον;
\versification{15}
συντέλειαν
ἐν
ἀγκίστρῳ
ἀνέσπασε
καὶ
εἵλκυσεν
αὐτὸν
ἐν
ἀμφιβλήστρῳ
καὶ
συνήγαγεν
αὐτὸν
ἐν
ταῖς
σαγήναις
αὐτοῦ.
\versification{16}
ἕνεκεν
τούτου
εὐφρανθήσεται
καὶ
χαρήσεται
ἡ
καρδία
αὐτοῦ·
ἕνεκεν
τούτου
θύσει
τῇ
σαγήνῃ
αὐτοῦ
καὶ
θυμιάσει
τῷ
ἀμφιβλήστρῳ
αὐτοῦ,
ὅτι
ἐν
αὐτοῖς
ἐλίπανε
μερίδα
αὐτοῦ,
καὶ
τὰ
βρώματα
αὐτοῦ
ἐκλεκτά.
\versification{17}
διὰ
τοῦτο
ἀμφιβαλεῖ
τὸ
ἀμφίβληστρον
αὐτοῦ
καὶ
διὰ
παντὸς
ἀποκτέννειν
ἔθνη
οὐ
φείσεται.

\subsect{Chapter 2}

\versification{1}
ἐπὶ
τῆς
φυλακῆς
μου
στήσομαι
καὶ
ἐπιβήσομαι
ἐπὶ
πέτραν
καὶ
ἀποσκοπεύσω
τοῦ
ἰδεῖν
τί
λαλήσει
ἐν
ἐμοὶ
καὶ
τί
ἀποκριθῶ
ἐπὶ
τὸν
ἔλεγχόν
μου.
\versification{2}
καὶ
ἀπεκρίθη
πρός
με
Κύριος
καὶ
εἶπε·
γράψον
ὅρασιν
καὶ
σαφῶς
εἰς
πυξίον,
ὅπως
διώκῃ
ὁ
ἀναγινώσκων
αὐτά.
\versification{3}
διότι
ἔτι
ὅρασις
εἰς
καιρὸν
καὶ
ἀνατελεῖ
εἰς
πέρας
καὶ
οὐκ
εἰς
κενόν·
ἐὰν
ὑστερήσῃ,
ὑπόμεινον
αὐτόν,
ὅτι
ἐρχόμενος
ἥξει
καὶ
οὐ
μὴ
χρονίσῃ.
\versification{4}
ἐὰν
ὑποστείληται,
οὐκ
εὐδοκεῖ
ἡ
ψυχή
μου
ἐν
αὐτῷ·
ὁ
δὲ
δίκαιος
ἐκ
πίστεώς
μου
ζήσεται.
\versification{5}
ὁ
δὲ
κατοιόμενος
καὶ
καταφρονητής,
ἀνὴρ
ἀλαζών,
οὐθὲν
μὴ
περάνῃ,
ὃς
ἐπλάτυνε
καθὼς
ᾅδης
τὴν
ψυχὴν
αὐτοῦ
καὶ
οὗτος
ὡς
θάνατος
οὐκ
ἐμπιπλάμενος
καὶ
ἐπισυνάξει
ἐπ᾿
αὐτὸν
πάντα
τὰ
ἔθνη
καὶ
εἰσδέξεται
πρὸς
αὐτὸν
πάντας
τοὺς
λαούς.
\versification{6}
οὐχὶ
ταῦτα
πάντα
κατ᾿
αὐτοῦ
παραβολὴν
λήψονται
καὶ
πρόβλημα
εἰς
διήγησιν
αὐτοῦ;
καὶ
ἐροῦσιν·
οὐαὶ
ὁ
πληθύνων
ἑαυτῷ
τὰ
οὐκ
ὄντα
αὐτοῦ
ἕως
τίνος;
καὶ
βαρύνων
τὸν
κλοιὸν
αὐτοῦ
στιβαρῶς.
\versification{7}
ὅτι
ἐξαίφνης
ἀναστήσονται
δάκνοντες
αὐτόν,
καὶ
ἐκνήψουσιν
οἱ
ἐπίβουλοί
σου,
καὶ
ἔσῃ
εἰς
διαρπαγὴν
αὐτοῖς.
\versification{8}
διότι
σὺ
ἐσκύλευσας
ἔθνη
πολλά,
σκυλεύσουσί
σε
πάντες
οἱ
ὑπολελειμμένοι
λαοὶ
δι᾿
αἵματα
ἀνθρώπων
καὶ
ἀσεβείας
γῆς
καὶ
πόλεως
καὶ
πάντων
τῶν
κατοικούντων
αὐτήν.
\versification{9}
ὦ
ὁ
πλεονεκτῶν
πλεονεξίαν
κακὴν
τῷ
οἴκῳ
αὐτοῦ
τοῦ
τάξαι
εἰς
ὕψος
νοσσιὰν
αὐτοῦ
τοῦ
ἐκσπασθῆναι
ἐκ
χειρὸς
κακῶν.
\versification{10}
ἐβουλεύσω
αἰσχύνην
τῷ
οἴκῳ
σου,
συνεπέρανας
πολλοὺς
λαούς,
καὶ
ἐξήμαρτεν
ἡ
ψυχή
σου·
\versification{11}
διότι
λίθος
ἐκ
τοίχου
βοήσεται,
καὶ
κάνθαρος
ἐκ
ξύλου
φθέγξεται
αὐτά.
\versification{12}
οὐαὶ
ὁ
οἰκοδομῶν
πόλιν
ἐν
αἵμασι
καὶ
ἑτοιμάζων
πόλιν
ἐν
ἀδικίαις.
\versification{13}
οὐ
ταῦτά
ἐστι
παρὰ
Κυρίου
παντοκράτορος;
καὶ
ἐξέλιπον
λαοὶ
ἱκανοὶ
ἐν
πυρί,
καὶ
ἔθνη
πολλὰ
ὠλιγοψύχησαν.
\versification{14}
ὅτι
ἐπλησθήσεται
ἡ
γῆ
τοῦ
γνῶναι
τὴν
δόξαν
Κυρίου,
ὡς
ὕδωρ
κατακαλύψει
αὐτούς.
\versification{15}
ὦ
ὁ
ποτίζων
τὸν
πλησίον
αὐτοῦ
ἀνατροπῇ
θολερᾷ
καὶ
μεθύσκων,
ὅπως
ἐπιβλέπῃ
ἐπὶ
τὰ
σπήλαια
αὐτῶν.
\versification{16}
πλησμονὴν
ἀτιμίας
ἐκ
δόξης
πίε
καὶ
σύ,
καρδία
σαλεύθητι
καὶ
σείσθητι·
ἐκύκλωσεν
ἐπὶ
σὲ
ποτήριον
δεξιᾶς
Κυρίου
καὶ
συνήχθη
ἀτιμία
ἐπὶ
τὴν
δόξαν
σου.
\versification{17}
διότι
ἀσέβεια
τοῦ
Λιβάνου
καλύψει
σε,
καὶ
ταλαιπωρία
θηρίων
πτοήσει
σε
δι᾿
αἵματα
ἀνθρώπων
καὶ
ἀσεβείας
γῆς
καὶ
πόλεως
καὶ
πάντων
τῶν
κατοικούντων
αὐτήν.
\versification{18}
τί
ὠφελεῖ
γλυπτόν,
ὅτι
ἔγλυψαν
αὐτό;
ἔπλασεν
αὐτὸ
χώνευμα,
φαντασίαν
ψευδῆ,
ὅτι
πέποιθεν
ὁ
πλάσας
ἐπὶ
τὸ
πλάσμα
αὐτοῦ
τοῦ
ποιῆσαι
εἴδωλα
κωφά.
\versification{19}
οὐαὶ
ὁ
λέγων
τῷ
ξύλῳ·
ἔκνηψον,
ἐξεγέρθητι,
καὶ
τῷ
λίθῳ·
ὑψώθητι·
καὶ
αὐτό
ἐστι
φαντασία,
τοῦτο
δέ
ἐστιν
ἔλασμα
χρυσίου
καὶ
ἀργυρίου,
καὶ
πᾶν
πνεῦμα
οὐκ
ἔστιν
ἐν
αὐτῷ.
\versification{20}
ὁ
δὲ
Κύριος
ἐν
ναῷ
ἁγίῳ
αὐτοῦ·
εὐλαβείσθω
ἀπὸ
προσώπου
αὐτοῦ
πᾶσα
ἡ
γῆ.



